### 2020-12-09 Thesis-Chapter1-Introduction.tex
Spruce up title, clean up Tools chapter

This thesis aims to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.--focused history of encryption regulation, technology, and conflict, I introduce \acp{argmap} and threat
models using data flow diagrams. In the following chapters, I analyze strategies for tacking \acp{wicked-prob}, map the
\acl{EA} arguments in detail, and demonstrate the security risks with data flow diagrams and threat analysis, focusing
on one particular EA proposal. The thesis concludes with research and policy paths forward in light of valid arguments
and threats.

>>>>

This thesis aims to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.--focused history of encryption regulation, technology, and conflict, I analyze strategies for tacking
\acp{wicked-prob} and introduce \acp{argmap} and threat modeling with data flow diagrams. In the following chapters, I
map the \acl{EA} arguments in detail and demonstrate the security risks with data flow diagrams and threat analysis,
focusing on one particular EA proposal. The thesis concludes with research and policy paths forward in light of valid
arguments and threats.

### 2020-12-09 Thesis-Chapter2-Background.tex
Spruce up title, clean up Tools chapter

The problem of strong encryption and \acl{EA} exists in a technical, historical, and regulatory context. This chapter
introduces cryptography, summarizes the history of encryption and the ``crypto wars,'' lists relevant encryption
regulations, and lists prominent technical \ac{EA} proposals. It then introduces \acp{argmap} as a logical modeling
tool, and introduces threat modeling with data flow diagrams.

>>>>

The problem of strong encryption and \acl{EA} exists in a technical, historical, and regulatory context. This chapter
introduces cryptography, summarizes the history of encryption and the ``crypto wars,'' lists prominent technical \ac{EA}
proposals, and lastly overviews relevant laws and regulations.

### 2020-12-09 Thesis-Chapter3-PolicyMaking.tex
Work on DFD section and normalize captions
Spruce up title, clean up Tools chapter

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/OODA-classical.png}
  \caption[The Classical Analytic Method]{The Classical Analytic Method}
  \label{fig-classical-method}
\end{figure}

@@

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=0.55\linewidth]{dfds/build/OODA-muddling.png}
  \caption[The Incrementalist Method]{The Incrementalist Method}
  \label{fig-muddling-through}
\end{figure}

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-vanilla.png}
    \caption[The OODA Loop]{The OODA Loop}
    \label{fig-ooda-loop}
\end{figure}

@@

Traditional policymaking typically follows either a rational approach rooted in the scientific method, aiming to be
thorough and complete, or an intuitional approach rooted in evolutionary trial and error, humbly aiming only to take
steps in the right direction. Both approaches have their strengths, but neither is suited to the complex and
controversial nature of so-called ``\acp{wicked-prob}.'' The strategy proposed here relies on the goodwill participation
of all parties, who engage in ongoing research and debate that rejects easy answers, encourages flexible risk-based
solutions, and crystallizes discussion around specific proposals. \Acp{argmap} are one tool that may facilitate this
process. The result from a single iteration is an imperfect step forward based on implementing a particular proposal.
The result from many iterations is the breakdown of the problem into subproblems---some tame and inevitably some still
wicked. The tame subproblems can be addressed with the \ac{classical-method}, and the wicked subproblems, by now
restrained under a sound and agreeable strategy, can be addressed with \ac{incrementalism}.

@@

In the remainder of this thesis, I will apply this strategy through the use of \acp{argmap} to document elements of the
debate in \mychap{chap-arguments} and through creation of a threat model against which I analyze one specific proposal
in \mychap{chap-threatmodel}.

>>>>

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/OODA-classical.png}
  \caption{The Classical Analytic Method}
  \label{fig-classical-method}
\end{figure}

@@

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=0.55\linewidth]{dfds/build/OODA-muddling.png}
  \caption{Incrementalism}
  \label{fig-muddling-through}
\end{figure}

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-vanilla.png}
    \caption{The OODA Loop}
    \label{fig-ooda-loop}
\end{figure}

@@

Traditional policymaking typically follows either a rational approach rooted in the scientific method, aiming to be
thorough and complete, or an intuitional approach rooted in evolutionary trial and error, humbly aiming only to take
steps in the right direction. Both approaches have their strengths, but neither is suited to the complex and
controversial nature of so-called ``\acp{wicked-prob}.'' The strategy proposed here relies on the goodwill participation
of all parties, who engage in ongoing research and debate that rejects easy answers, encourages flexible risk-based
solutions, and crystallizes discussion around specific proposals. The result from a single iteration is an imperfect
step forward based on implementing a particular proposal. The result from many iterations is the breakdown of the
problem into subproblems---some tame and inevitably some still wicked. The tame subproblems can be addressed with the
\ac{classical-method}, and the wicked subproblems, by now restrained under a sound and agreeable strategy, can be
addressed with \ac{incrementalism}.

@@

In the remainder of this thesis, I apply this strategy by documenting the debate in depth in \mychap{chap-arguments} and
through creation of a threat model against which I analyze one specific proposal in \mychap{chap-threatmodel}.

### 2020-12-09 Thesis-Chapter4-Tools.tex
Spruce up title, clean up Tools chapter

% FIXME: include a more descriptive key to understand argument maps.

% - Prof. Dulimarta: Could you apply fuzzy logic to the argument map? Quantify it? -- I think this would run into limits
%   once you start comparing unquantifiable things, but it could be used to suss out the valid arguments, and would
%   probably be really interesting otherwise.

% Kalafut: I'm not sure that 2.5 and 2.6 really fit well as subsections of 2. Consider separating them into their own
% (short) chapter.
% Kalafut: Argument maps are used in chapter 4. I'm not sure that you need to mention argdown at all. If you do, I would
% only do so in the context of stating that it is the tool you are using to create argument maps.

@@

The arguments used in the \ac{EA} debate are diverse and complex; in order to advance the \ac{EA} discussion, it would
help to organize all the arguments used in a cohesive manner. One way to organize arguments is to create \acp{argmap}.
\Acp{argmap} are graphical representations of the logical structures and relationships between statements, premises, and
conclusions. \Acp{argmap} are an outgrowth of the same research by Horst Rittel that originated the idea of
\acp{wicked-prob}. In 1970 his research group developed \acp{IBIS} to break down \acp{wicked-prob} and document the
reasoned approaches that go into solving them \cite{kunz_issues_1970}. Interest in \ac{IBIS} has waxed and waned. Some
software tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and Compendium
\cite{dutoit_hypermedia_2006} tools designed to produce graphical representations. Argdown is a recent tool that
generates \acp{argmap} from structures specified in a Markdown-based language \cite{voigt_argdown_2018}.

Argdown is used in \mychap{chap-arguments} to analyze the arguments used in the \ac{EA} debate. \myfig{fig-args-demo}
shows the basic structure of arguments. Statements are positions on issues. Some statements are based on values that
cannot be addressed through argument. Statements and arguments may support or attack one another, and arguments support
or undercut other arguments.

\begin{figure}[ht]
    \centering\CaptionFontSize
    \myincludeargument{demo}
    \caption{A demonstrative example of argument maps with Argdown}
    \label{fig-args-demo}
\end{figure}

%%%%%%%%%%%%%%%%% Hack job

Recall from \mysec{sec-arg-maps-intro} that \acp{argmap} resulted from the same research that produced the concept of
\acp{wicked-prob}. Though formal research on the technique is thin, \acp{argmap} have proven helpful in simplifying
complex arguments around \acp{wicked-prob} \cite{renton_2007} and in facilitating debate by helpfully slowing down
discussion, depersonalizing conflict, and lending structure and rhythm \cite{dutoit_hypermedia_2006}. This makes them
well suited as a tool for conducting the collaborative debate that helps problem solvers with disparate views narrow in
on a problem definition and concrete proposals on which they can agree.

% FIXME: Kalafut: It's not clear to me that this paragraph is a good fit here. It is good content. Perhaps this
% paragraph or its ideas should be at the start of the Argument Maps section.
% PLAN: I will move this to when I talk more about argument maps. After the refactor, they won't even be introduced yet
% here.

\section{Threat Models and Data Flow Diagrams}
\label{sec-threat-model-intro}

@@

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.8\linewidth]{dfds/build/diffie-hellman-traditional.png}
    \caption{A \acf{DFD} for a simplified Diffie-Hellman key exchange}
    \label{fig-dfd-dh-traditional}
\end{figure}

@@

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/diffie-hellman.png}
    \caption{A Diffie-Hellman key exchange illustrated with additional syntax}
    \label{fig-dfd-dh-updated}
\end{figure}

@@

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.85\linewidth]{dfds/build/dfd-key.png}
    \caption{Expanded set of DFD symbols}
    \label{fig-dfd-key}
\end{figure}

>>>>

Encryption policy arguments and \acl{EA} threat models are complex. \Acp{argmap} and \aclp{DFD} two methodological tools
to structure analysis and reduce complexity. This chapter introduces these tools and their syntax as used in
\mychap{chap-arguments} and \mychap{chap-threatmodel}.

@@

The arguments used in the \ac{EA} debate are diverse and complex; in order to advance the \ac{EA} discussion, it would
help to organize all the arguments used in a cohesive manner. One way to organize arguments is to create \acp{argmap}.
\Acp{argmap} are graphical representations of the logical structures and relationships between statements, premises, and
conclusions. \Acp{argmap} are an outgrowth of the same research by Horst Rittel that originated the idea of
\acp{wicked-prob}. Though formal research on the technique is thin, \acp{argmap} have proven helpful in simplifying
complex arguments around \acp{wicked-prob} \cite{renton_2007} and in facilitating debate by helpfully slowing down
discussion, depersonalizing conflict, and lending structure and rhythm \cite{dutoit_hypermedia_2006}. This makes them
well suited as a tool for conducting the collaborative debate that helps problem solvers with disparate views narrow in
on a problem definition and concrete proposals on which they can agree.

In 1970 Rittel's research group developed \acp{IBIS} to break down \acp{wicked-prob} and document the reasoned
approaches that go into solving them \cite{kunz_issues_1970}. Interest in \ac{IBIS} has waxed and waned. Some software
tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and Compendium
\cite{dutoit_hypermedia_2006} tools designed to produce graphical representations. Argdown is a recent tool that
generates \acp{argmap} from structures specified in a Markdown-based language \cite{voigt_argdown_2018}. Argdown is used
in \mychap{chap-arguments} to analyze the arguments used in the \ac{EA} debate.

\myfig{fig-args-key} shows the basic structure of arguments. Statements are positions, values, and assertions. The
``Proposals,'' ``Statements,'' ``Fallacies,'' and ``Values'' in the figure are classes of statements in this sense. The
color of a statement's border indicates the class to which it belongs. Arguments are premise-conclusion structures that
relate to statements. Arguments as classified as ``anti-EA,'' ``pro-EA,'' ``neutral,'' or ``fallacious.'' The color of
an argument's solid background indicates the class to which it belongs. Statements and arguments may support, attack, or
undercut one another. Supporting relationships have green arrows; attacking, red; and undercutting, purple.

\begin{figure}[h]
    \centering\CaptionFontSize
    \myincludeargument{key}
    \caption{A demonstrative example of argument maps with Argdown}
    \label{fig-args-key}
\end{figure}

\section{Threat Modeling with Data Flow Diagrams}
\label{sec-threat-model-intro}

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=0.8\linewidth]{dfds/build/diffie-hellman-traditional.png}
    \caption{A \acf{DFD} for a simplified Diffie-Hellman key exchange}
    \label{fig-dfd-dh-traditional}
\end{figure}

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/diffie-hellman.png}
    \caption{A Diffie-Hellman key exchange illustrated with additional syntax}
    \label{fig-dfd-dh-updated}
\end{figure}

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=0.85\linewidth]{dfds/build/dfd-key.png}
    \caption{Expanded set of DFD symbols}
    \label{fig-dfd-key}
\end{figure}
